One more attempt on ArXe

### 2015-11-11 exp_results.tex
started discussion of valence spectra, minor edits in introduction, theory results

\section{Experimental Results}

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The experimental Xe content of the clusters (Xe$_{\rm cl}$) always is higher than in the original gas mixture (Xe$_{\rm in}$). Xe$_{\rm cl}$ was determined from the areas of the respective photolines, corrected by the respective atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. $\EB$ and $w$ are in eV. The theoretical Ar 3p binding energy, averaged over fine structure, amounts to 15.27 eV.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ & $w$& \multicolumn{2}{c}{$\EB$}  & $w$ &  Xe$_{cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & (Ar 3p) & (Ar 3p) & (Xe 5p$_{1/2}$) &  (Xe 5p$_{3/2}$) & (Xe 5p$_{3/2}$)  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
%
 Ar, Xe & th.\cite{Fasshauer13} && 14.76|15.53 && 12.53 & 10.83 &&\\
%
 \multicolumn{2}{r}{atomic\cite{velchev,sansonetti}} && 15.82 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). The two lower panels show the spectra of the mixed species of different size. Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters. The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
}
 \label{figure:oval1}
\end{figure}

@@

>>>>

\section{Experimental Results
\label{sec:exp_results}}

\begin{table}
\caption{Properties of the outer valence spectra of mixed ArXe clusters. Spectra of pure Ar and Xe clusters are included for reference. All spectra were recorded at $h\nu = 17$~eV, except for the pure Xe clusters ($h\nu = 60$~eV). Binding energies $\EB$ were determined as the centre of gravity of the respective feature, while band width $w$ are the FWHM of a Gaussian fit. The Xe content of the clusters (Xe$_{\rm cl}$) always is higher than in the original gas mixture (Xe$_{\rm in}$). Xe$_{\rm cl}$ was determined from the areas of the respective photolines, corrected by their atomic photoionization cross sections (Ar 33.0 Mb, Xe 51.3 Mb)\cite{samson2002}. $\EB$ and $w$ are in eV. Uncertainties are estimated as 3\,\% for the Xe content and 0.05~eV for the binding energies. For reference, the row labelled `(th.)' gives the binding energies used in the simulations of this paper (same as in Ref. \citenum{Fasshauer13}), and the last row their atomic counterparts.
\label{tab:valence} }
\begin{tabular}{ l c c c c c c c c}
%
\toprule
 \multicolumn{2}{r}{size} &  Xe$_{in}$& $\EB$ & $w$& \multicolumn{2}{c}{$\EB$}  & $w$ &  Xe$_{\rm cl}$ \\
%
 \multicolumn{2}{r}{(label)}&  (\%) & (Ar 3p) & (Ar 3p) & (Xe 5p$_{1/2}$) &  (Xe 5p$_{3/2}$) & (Xe 5p$_{3/2}$)  &  (\%) \\
\midrule
% Ar, from Marko
 Ar & (1) &&  15.3  &  1.1 & & & &  \\
% Ar, from Marko 
 Ar & (2) &&  15.1  &  1.3 & & & &  \\
%
%  columns in the following: energies c.g. 51-plt-oval, widths Marko Diss., Xe content Marko Diss
% 1103 676, 679
 ArXe & S &1.2 & 15.36 & 0.9 & 13.07 & 11.75 & 0.85 & 12\\
% 1103 670
 ArXe & M &1.2 & 15.30 & 1.0 & 12.97 & 11.61 & 0.85 & 11\\
% 1103 671
 ArXe & L &1.2 & 15.25 & 1.1 & 12.91 & 11.52 & 1.08 & 10\\
% 1103 663
 ArXe & S &3.0 & 15.39 & 0.8 & 13.06 & 11.68 & 1.02 & 29\\
% 1103 640
 ArXe & M &5.0 & 15.31 & 0.6 & 12.96 & 11.44 & 1.24 & 53\\
% 0506 
 Xe &  & & & & 12.76 & 11.19 & 1.18 & 100\\
%
\midrule
%
%  1004  886  (UHe, c.g. + roi values)
 ArXe & XL &2.5 & 15.15 & 1.3 & 12.59 & 11.01 & 1.24 & 19\\
%
\midrule
%
 Ar, Xe & (th.) && 14.76|15.53 && 12.53 & 10.83 &&\\
%
 \multicolumn{2}{l}{(atomic)\cite{velchev,sansonetti}} && 15.76|15.94 && 13.43 & 12.13 &&\\
%
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
Outer valence photoelectron spectra of mixed Ar-Xe clusters, in comparison to the pure species. Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). The two lower panels show spectra of the mixed species with different mean size. Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters. The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
}
 \label{figure:oval1}
\end{figure}

@@

Figure \ref{figure:oval1} shows the outer valence spectra of small and large ArXe clusters, compared to clusters of the pure gases. Differences are seen in particular for the Ar component. In pure Ar clusters, outer valence photoionization leads to a broad band, caused both by spin-orbit coupling and crystal field splitting. The relative importance of these two mechanisms remains under debate.\cite{hergenhahnprb,rolles} At the particular photon energy selected here, atop of this band a sharp feature is also visible (in Figure \ref{figure:oval1} at a kinetic energy of about 1.8 eV). For larger clusters, this shows a dispersion characteristic for photoionization of crystalline bulk matter.\cite{foerstel_arg1_2010,foerstel_arg2_2011}

### 2015-11-11 experimental.tex
tweek theoretical pictures to show up in the text
started discussion of valence spectra, minor edits in introduction, theory results

\begin{tabular}{l c c c c r r}
%
\toprule
  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar & (1) & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar & (2) & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
ArXe & S & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
ArXe & M & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
ArXe & L & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
ArXe & S & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
ArXe & M & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe &  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
ArXe & M & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
ArXe & L & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
ArXe & S  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
ArXe & L  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 867 (32 eV)
ArXe & XL & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886 (17 eV)
%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table}
%
%
The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} 
% Leave this citation in place to avoid Latex error
A detailed description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
Expansion parameters and mean cluster sizes, according to an empirical model, are given in Tab.\ \ref{tab:cluster}. 
We note that currently no empirical model for cluster sizes in a heterogeneous gas expansion exists. 
We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions.

The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). 
At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} 
Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Tab.\ \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Tab.\ \ref{tab:cluster}). 
Linearly, horizontally polarized radiation was used. 
The storage ring was operated in single bunch conditions.

>>>>

\begin{tabular}{l c c c c r r}
%
\toprule
  \multicolumn{2}{r}{size label}  &  Xe$_{\rm in}$ (\%)  &  $T$ (K)  &  $p$ (bar) & $\langle N_{\rm Ar} \rangle$ & $\langle N_{\rm Xe} \rangle$ \\
%
\midrule
% Ar, from Marko 
Ar & (1) & --- &  96.5  & 0.35  &  42  &  --- \\
% Ar, from Marko 
Ar & (2) & --- &  96.5  & 0.67  & 190  &  --- \\
% 1103 676, 679
ArXe & S & 1.2 &  174   & 0.32  &   4  &   62 \\
% 1103 670
ArXe & M & 1.2 &  174   & 0.49  &  10  &  168 \\
% 1103 671
ArXe & L & 1.2 &  174   & 0.68  &  21  &  362 \\
% 1103 663
ArXe & S & 3.0 &  172   & 0.28  &   3  &   48 \\
% 1103 640
ArXe & M & 5.0 &  171   & 0.51  &  12  &  202 \\
% 0506 382, Keller offset ber?cksichtigt
Xe &  & 100 & 183.5  & 0.68  & ---  &  517 \\     
\midrule
% 1103 653
ArXe & M & 3.0 &  172   & 0.51  &  11  &  196 \\
% 1103 658
ArXe & L & 3.0 &  172   & 0.68  &  22  &  385 \\
% 1103 630
ArXe & S  & 5.0 &  167   & 0.37  &   6  &  108 \\
% 1103 629
ArXe & L  & 5.0 &  167   & 0.68  &  26  &  451 \\
\midrule
% 1004 867 (32 eV)
ArXe & XL & 2.5 &  154   & 2.12  &  920 & 15760\\
% 1004 868
%868 & & 2.5 &  158   & 1.50  &  355 &  6090\\
% 1004 886 (17 eV)
%886 &  & 2.5 &  161   & 2.41  &  980 & 16770\\
% 1004 858
%858 &  & 5.0 &  149   & 2.50  & 1620 & 27700\\
%
\bottomrule
\end{tabular}
\end{table}
%
%
The apparatus used for the experiments consists of a supersonic molecular jet with a cooled nozzle, and a magnetic bottle spectrometer, which detects photoelectrons and secondary electrons produced after ionization with synchrotron radiation.\cite{arion} 
% Leave this citation in place to avoid Latex error
A detailed description can be found in Ref. \citenum{arion}, and here we focus on details specific for the current experiment. Commercial Ar and Xe gas was used. 
Separate containers for the two gases were filled up to pressures suitable for producing a certain mixing ratio. The gases were then allowed to mix before the expansion. 
Expansion parameters and mean cluster sizes are given in Table \ref{tab:cluster}. 
Currently, no model to predict cluster sizes in a heterogeneous gas expansion exists. 
We therefore can only give the mean size for a pure jet of one or the other gas at the given conditions, which we have derived according to an empirical scaling law.\cite{hagena1981} 
We note that recent analyses of photoionization spectra suggests that  mean sizes arrived at by scaling laws are smaller than the actual size, at least for rare gas clusters.\cite{bergersen,hergenhahnprb,foerstel_arg2_2011}

The expansion chamber for the supersonic jet is separated from the interaction chamber by a non-magnetic, conical skimmer with a diameter 1~mm opening (Beam Dynamics). 
At few cm distance behind the skimmer, the cluster jet was crossed by synchrotron radiation from the BESSY electron storage ring at Helmholtz-Zentrum Berlin. 
Electrons were detected by a short `magnetic bottle' time-of-flight spectrometer, that has been described earlier.\cite{mucke_review} 
Data were recorded in two different beamtimes at the UE112-PGM-1 (small and medium sized clusters, first two sections in Table \ref{tab:cluster}) and at the TGM-4 beamline (large clusters, last section in Table \ref{tab:cluster}). 
Linearly, horizontally polarized radiation was used. 
The storage ring was operated in single bunch conditions.

### 2015-11-11 theo_results.tex
started discussion of valence spectra, minor edits in introduction, theory results

\section{Theoretical Results}
%
%
\begin{table}[h]
\centering
\caption{Calculated properties of some model clusters. ICD, ETMD, and
are the respective partial decay widths
in \unit[$10^{-4}$]{eV} and \% ICD gives the ICD percentage of the
total decay width.
}
\begin{tabular}{lrrrccr}
\toprule
name                 & Xe atoms & Ar atoms & Xe \% & ICD   &  ETMD & \% ICD\\ %$\Gamma_{\rm ICD,ETMD}$\\
\midrule
ArXe\_2\_1atom       &      1   &     12   &  7.7  & 0.000 & 0.000 &  --\\ %    0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  & 0.000 & 0.000 &  --\\ %    0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 0.033 & 0.167 &  16.7\\ %2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039 & 2.573 &  73.2\\ %9.612$\cdot 10^{-4}$ \\
\midrule
XeAr\_2\_surface     &      1   &     13   &  7.1  & 0.792 & 0.000 & 100.0\\ %7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 0.013 & 0.000 & 100.0\\ %1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 0.050 & 0.000 & 100.0\\ %5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 0.101 & 0.151 &  40.1\\ %2.523$\cdot 10^{-5}$ \\
XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 0.159 & 0.008 &  95.4\\ %1.665$\cdot 10^{-5}$ \\
XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 0.159 & 0.002 &  98.9\\ %1.605$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 0.064 & 0.000 & 100.0\\ %6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 0.048 & 0.000 & 100.0\\ %4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 0.027 & 0.000 & 100.0\\ %2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 0.077 & 0.000 & 100.0\\ %7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 0.053 & 0.000 & 100.0\\ %5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 0.117 & 0.055 &  68.1\\ %1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 0.375 & 0.405 &  48.1\\ %7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 0.292 & 0.674 &  30.3\\ %9.660$\cdot 10^{-5}$ \\
\bottomrule
\end{tabular}
\label{table:theo_gammas}
\end{table}
%
The geometrical properties as well as the total ICD and ETMD decay widths
of the investigated structures are shown in Table \ref{table:theo_gammas}.
It is important to remember that the first ICD channel opens at a
channel opening distance of \unit[7.58]{\AA}. In small
clusters, are Ar-Xe pair distances are below that value, therefore 
no ICD can take place. Also, by definition two Xe atoms are
required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
%Because secondary electrons are observed in the experimental spectra
%we exclude all structures without any signal from our further
%discussions.
%
%In the investigated structures several different aspects have to be
%taken into account which we will discuss separately if possible
%on selected structures.

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/2tops.pdf}
 \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters consisting of 13
          argon atoms with 2 additional xenon atoms on top of two different
          argon surfaces. ICD and ETMD spectra are shown for three
          different relative positions of the two xenon atoms. If 
          the xenon atoms are close to each other, an ETMD process is
          clearly visible. In the other two cases the spectra are dominated by
          the ICD spectrum.
          {\it Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
 \label{figure:2tops}
\end{figure}
%
For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peak due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the lower are the energies
of the secondary electrons and the smaller are the decay widths. 
{\it Q: war: `the higher are the decay widths', falschrum, oder?}
Therefore a
significant contribution from the ETMD(3) compared to the ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The threefold peak structure of the ETMD(3) peak does in contrast to
the ICD spectrum not stem from different triple structures but from the
four different decay channels for one triple structure.

@@

Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
the ICD peak is broadened and shifted to higher ICD electron energies which is
expected due to the larger interatomic Ar-Xe distances in the large cluster and
the better stabilization of charges (the final state), which has been taken into account
in the simulation.
The ETMD(3) peak is shifted to slightly higher energies as well, which allows opening of the
fourth decay channel.

>>>>

\section{Theoretical Results}
%
%
\begin{table}[h]
\centering
\caption{Calculated properties of some model clusters. ICD, ETMD, and $\Gamma_{\rm ICD, ETMD}$ are the respective partial and total decay widths in 
{\it Q: Einheit von $\Gamma$? 
Ich schlage vor, alle Zerfallsbreiten mit einem festen Exponenten von z.B. 10$^{-6}$ aufzuschreiben, und diesen wegzulassen. 
Die Tabelle w\"urde dadurch \"ubersichtlicher, und man sieht gleich welche Zerf\"alle \"uberhaupt wichtig sind.
Ich schlage weiterhin vor, statt $\Gamma_{\rm ICD, ETMD}$ das ratio $\Gamma_{\rm ETMD}/\rm total$ zu zeigen (ist glaube ich n\"utzlicher f\"ur die Diskussion).}
}
\begin{tabular}{lrrrccc}
\toprule
name                 & Xe atoms & Ar atoms & Xe \% &   ICD                &  ETMD                & $\Gamma_{\rm ICD,ETMD}$\\
\midrule
ArXe\_2\_1atom       &      1   &     12   &  7.7  &      0.0             &  0.0                 &     0.0            \\
ArXe\_3\_1atom       &      1   &     54   &  1.8  &      0.0             &  0.0                 &     0.0            \\ 
ArXe\_3\_2atom       &      2   &     53   &  3.6  & 3.346$\cdot 10^{-6}$ & 1.666$\cdot 10^{-5}$ & 2.006$\cdot 10^{-5}$ \\
ArXe\_8\_1layer      &   1415   &    642   & 68.8  & 7.039$\cdot 10^{-4}$ & 2.573$\cdot 10^{-4}$ & 9.612$\cdot 10^{-4}$ \\
\midrule
XeAr\_2\_surface     &      1   &     13   &  7.1  & 7.922$\cdot 10^{-5}$ & 0.0                  & 7.922$\cdot 10^{-5}$ \\
XeAr\_2\_edge        &      1   &     13   &  7.1  & 1.320$\cdot 10^{-6}$ & 0.0                  & 1.320$\cdot 10^{-6}$ \\
XeAr\_2\_vertex      &      1   &     13   &  7.1  & 5.013$\cdot 10^{-6}$ & 0.0                  & 5.013$\cdot 10^{-6}$ \\
XeAr\_2\_2top        &      2   &     13   & 13.3  & 1.011$\cdot 10^{-5}$ & 1.513$\cdot 10^{-5}$ & 2.523$\cdot 10^{-5}$ \\
XeAr\_2\_2midtop     &      2   &     13   & 13.3  & 1.588$\cdot 10^{-5}$ & 7.686$\cdot 10^{-7}$ & 1.665$\cdot 10^{-5}$ \\
XeAr\_2\_2endtop     &      2   &     13   & 13.3  & 1.587$\cdot 10^{-5}$ & 1.772$\cdot 10^{-7}$ & 1.605$\cdot 10^{-5}$ \\
XeAr\_3\_surface     &      1   &     55   &  1.8  & 6.371$\cdot 10^{-6}$ & 0.0                  & 6.371$\cdot 10^{-6}$ \\
XeAr\_3\_edge        &      1   &     55   &  1.8  & 4.791$\cdot 10^{-6}$ & 0.0                  & 4.791$\cdot 10^{-6}$ \\
XeAr\_3\_vertex      &      1   &     55   &  1.8  & 2.701$\cdot 10^{-6}$ & 0.0                  & 2.701$\cdot 10^{-6}$ \\
XeAr\_3\_edge\_in    &      1   &     54   &  1.8  & 7.708$\cdot 10^{-6}$ & 0.0                  & 7.708$\cdot 10^{-6}$ \\
XeAr\_3\_vertex\_in  &      1   &     54   &  1.8  & 5.258$\cdot 10^{-6}$ & 0.0                  & 5.258$\cdot 10^{-6}$ \\
XeAr\_3\_2in         &      2   &     53   &  3.6  & 1.166$\cdot 10^{-5}$ & 5.453$\cdot 10^{-6}$ & 1.711$\cdot 10^{-5}$ \\
XeAr\_3\_6in         &      6   &     49   & 10.9  & 3.746$\cdot 10^{-5}$ & 4.050$\cdot 10^{-5}$ & 7.796$\cdot 10^{-5}$ \\
XeAr\_3\_6\_scat     &      6   &     49   & 10.9  & 2.923$\cdot 10^{-5}$ & 6.737$\cdot 10^{-5}$ & 9.660$\cdot 10^{-5}$ \\
\bottomrule
\end{tabular}
\label{table:theo_gammas}
\end{table}
%
The geometrical properties as well as the total ICD and ETMD decay widths
of the investigated structures are shown in Table \ref{table:theo_gammas}.
It is important to remember that the first ICD channel opens at a
channel opening distance of \unit[7.58]{\AA}. In small
clusters, are Ar-Xe pair distances are below that value, therefore 
no ICD can take place. Also, by definition two Xe atoms are
required for ETMD(3), hence it cannot occur in clusters with only one xenon atom.
%Because secondary electrons are observed in the experimental spectra
%we exclude all structures without any signal from our further
%discussions.
%
%In the investigated structures several different aspects have to be
%taken into account which we will discuss separately if possible
%on selected structures.

@@

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/2tops.pdf}
 \caption{Simulated electron emission spectra of an Ar 3s vacancy in 
          argon clusters consisting of 13
          argon atoms with 2 additional xenon atoms on top of two different
          argon surfaces. ICD and ETMD spectra are shown for three
          different relative positions of the two xenon atoms. If 
          the xenon atoms are close to each other, an ETMD process is
          clearly visible. In the other two cases the spectra are dominated by
          the ICD spectrum.
          {\it Q: Warum ist in diesen (und vielen anderen) Bildern jedes Label doppelt?}}
 \label{figure:2tops}
\end{figure}
%
For clusters with more than one xenon atom, also ETMD(3) is possible.
Depending on the positions of the xenon atoms relative to each other and to the Ar core, the spectra are expected to be different.
As an example, we discuss clusters with a core of 13 argon atoms and two xenon atoms on different surfaces. 
Their xenon content is \unit[13.3]{\%} and thus close to the experimental one of \unit[10-12]{\%} for the lowes xenon admixture.
The cluster structures were illustrated in Figure \ref{figure:cluster_2_overview}, simulated spectra are shown in Figure \ref{figure:2tops}.
In all three cases, both ICD and ETMD(3) are energetically allowed. The ICD
spectra do not change qualitatively by adding the second xenon.
%either identical or at least very similar to the ones for
%cluster with a single  consisting of one
%convoluted peak at approximately \unit[0.2]{eV}. 
However, the ETMD(3) spectra
are very sensitive to the relative position of the two xenon atoms.
Two aspects have to be taken into account: an energy shift of the peaks due
to different charge distances in the final state (i.e. the interatomic Xe-Xe
distance) and the decrease of the decay width with $R^{-6}$, $R$ being the distance
between the electron transfer unit and the xenon atom ionized in the final state.
The larger the distance between the xenon atoms, the lower are the energies
of the secondary electrons and the smaller are the decay widths. 
{\it Q: war: `the higher are the decay widths', falschrum, oder?}
Therefore, a
significant contribution from ETMD(3) compared to ICD is only
seen if the two xenon atoms reside on two adjacent
surfaces. 
%{\it Q: Ich verstehe nicht was der n\"chste Satz sagen soll.}
The three energetically separated peaks in the ETMD(3) spectrum pertain to different combinations of the Xe 5p$_j^{-1}$ vacancy states, which have a substantial fine-structure splitting (see \ref{sec:exp_results}).
%
%The threefold peak structure of the ETMD(3) peak does in contrast to
%the ICD spectrum not stem from different triple structures but from the
%four different decay channels for one triple structure.

@@

Compared to the small clusters with a xenon core in Figure \ref{figure:xe_3_in}
the ICD peak is broadened and shifted to higher ICD electron energies which is
expected due to the larger interatomic Ar-Xe distances in the large cluster and
the better stabilization of charges (the final state), which has been taken into account
in the simulation.
The ETMD(3) peak is shifted to slightly higher energies as well. This allows opening of the
fourth decay channel, pertaining to Xe 5p$_{1/2}^{-1}$ Ar 3p$_{1/2}^{-1}$ final states.
